---
title: "Import"
author: "M Schmettow"
date: "19/02/2021"
output: html_document
---

```{r setup}
library(tidyverse)
library(lubridate)
library(bayr)
library(esmerald)
```

# Import

Character vector of csv files

```{r}
csv <- dir("../inst/extdata/",full.names = T)[1:8]
```

Reading a single file

```{r}
ESM_1 <- read_ethica_csv(csv[2])
```

The result is a table of class *tbl_esm*.

```{r}
class(ESM_1)
```

But the fact that we use S3 classes shouldn't bother you. It just makes it easier for us to create a convenient interface. For example, if you just call the ESM_1 object like this:

```{r eval = F}
ESM_1
```

you get a summary of the data set:

```{r echo = F}
ESM_1
```

ESM_1 is in long format. Every measure gets its own row. The long format also makes it very easy to combine a group of files into one ESM table. If you know a little programming already, you might think that processing a list of objects requires a loop. In R, this is much easier. `map_df` takes a list of file names as input, applies the function `read_ethica_csv` a number of times and merges the results into  one ESM table.


```{r}
ESM_2 <- csv[2:6] %>% map_df(read_ethica_csv)
ESM_2
```
The `plot` command provides an overview of the data.

```{r fig.height = 12}
plot(ESM_2)
```




